Figures and results for main manuscript

### 2021-03-17 analysis/rev_prototyping/manuscript_main_rev.Rmd
figs

---
title: "Figures and results for main manuscript"
author: Renata Diaz
date: "`r Sys.Date()`"
output: 
    github_document:
       df_print: kable
---

@@

```{r first hists, fig.dim = c(9,5)}

@@

plot_percentile_hist(all_di, "real_po_percentile_mean", "Dissimilarity to the \ncentral tendency", facetvar = "Dataset", tails = 1),
  plot_percentile_hist(all_di, "nsingletons_percentile_mean", "\nNumber of rare species", facetvar = "Dataset"),
  plot_percentile_hist(all_di, "skew_percentile_mean", "\nSkewness", facetvar = "Dataset", min_s0 = 3),
   plot_percentile_hist(all_di, "simpson_percentile_mean", "\nSimpson evenness", facetvar = "Dataset")#,
  # plot_percentile_hist(all_di, "shannon_percentile_mean", "\nShannon diversity", facetvar = "Dataset")
  ), ncol = 4,
top = textGrob("Figure 2", gp = gpar(fill = "white")), left = textGrob("Number of communities", rot = 90, gp = gpar(fill = "black")),
bottom = textGrob("Percentile rank of observed value relative to feasible set"), gp = gpar(fill = "white"))
```

@@

  if(grepl("sim_pos", yvar)) {
    min_nparts = 20
  } else {
    min_nparts = 40
  }

@@

  ggplot(di_df, aes(nparts, response, color = Dataset)) +
  geom_point(alpha = .3) +
  geom_point(data = filter(di_df, s0 < 0)) +
  scale_color_viridis_d(end = .9) +
  xlab("") +
  ylab("") +
  scale_x_log10() +
  ggtitle(yvar_name) + 
    theme(legend.position = "none")+ 
    theme(plot.title = element_text(size=10))
}

@@

gridExtra::grid.arrange(grobs = list(
  plot_narrowness(all_di, "sim_pos_from_best", "Dissimilarity \nto central tendency") + theme(legend.position = "bottom", legend.direction = "vertical" , legend.margin = margin(b = .5, r = 0, t = 0, l = 0, unit = "in")
), gridExtra::grid.arrange(grobs = list(
  plot_narrowness(all_di, "skew_95_ratio_2t", "\nSkewness"),
  plot_narrowness(all_di, "simpson_95_ratio_2t", "\nSimpson evenness"),
    plot_narrowness(all_di, "shannon_95_ratio_2t", "\nShannon diversity"),
    plot_narrowness(all_di, "nsingletons_95_ratio_2t", "\nNumber of rare species")
  ), ncol = 2)), ncol = 2, widths = c(2, 4))

@@

<!-- # Breadth index by dataset (Figure 3) -->

<!-- ```{r, fig.dim = c(7,7)} -->

<!-- fig_3 <- gridExtra::grid.arrange(grobs = list( -->
<!--   ggplot(filter(all_di, s0 > 2, nparts > 20), aes(x= skew_95_ratio_1t)) + -->
<!--     geom_histogram() + -->
<!--     theme_bw() + -->
<!--     facet_wrap(vars(Dataset), scales = "free_y", ncol = 1) + -->
<!--     xlab("") + -->
<!--     ylab("") + -->
<!--     ggtitle("Skewness") + -->
<!--     xlim(0, 1), -->

<!--   ggplot(filter(all_di, nparts > 20), aes(x = simpson_95_ratio_1t)) + -->
<!--     geom_histogram() + -->
<!--     theme_bw() + -->
<!--     facet_wrap(vars(Dataset), scales = "free_y", ncol = 1) + -->
<!--     xlab("") + -->
<!--     ylab("") + -->
<!--     ggtitle("Evenness") + -->
<!--     xlim(0, 1) -->
<!-- ), ncol = 2, -->
<!-- top = textGrob("Figure 3", gp = gpar(fill = "white")), -->
<!-- left = "Number of communities",  -->
<!-- bottom = "Breadth index (ranges 0-1, with 1 being very broad)") -->

<!-- plot(fig_3) -->

<!-- ``` -->

<!-- # Comparison of FIA and comparably sized communities (Figure 4) -->

<!-- ```{r, fig.dim = c(7,7)} -->

<!-- fia_max_s = max(filter(all_di, dat == "fia")$s0) -->
<!-- fia_max_n = max(filter(all_di, dat == "fia")$n0) -->

<!-- fia = filter(all_di, dat == "fia") -->

<!-- small_di <- all_di %>% -->
<!--   filter(s0 <= fia_max_s, -->
<!--          n0 <= fia_max_n) %>% -->
<!--   mutate(fia_yn = ifelse(dat == "fia", "fia", "other datasets"), -->
<!--          right_corner = FALSE) -->

<!-- for(i in 1:nrow(small_di)) { -->
<!--   if(small_di$dat[i] != "fia") { -->
<!--     fia_match_s0 = filter(fia, s0 >= small_di$s0[i]) -->

<!--     max_n0_for_this_s0 = max(fia_match_s0$n0) -->

<!--     small_di$right_corner[i] = small_di$n0[i] > max_n0_for_this_s0 -->

<!--   } -->
<!-- } -->

<!-- small_di <- small_di %>% -->
<!--   filter(!right_corner) -->
<!-- not_fia <- filter(small_di, fia_yn != "fia") -->
<!-- fia = filter(small_di, dat == "fia") -->

<!-- small_di_s_n <- small_di %>% -->
<!--   select(s0, n0) %>% -->
<!--   distinct() %>% -->
<!--   mutate(in_fia = FALSE, -->
<!--          in_not_fia = FALSE) -->

<!-- for(i in 1:nrow(small_di_s_n)) { -->

<!--   this_s0 = small_di_s_n$s0[i] -->
<!--   this_n0 = small_di_s_n$n0[i] -->

<!--   fia_matches = filter(fia, s0 == this_s0, n0 == this_n0) -->
<!--   not_fia_matches = filter(not_fia, s0 == this_s0, n0 == this_n0) -->

<!--   small_di_s_n$in_fia[i] = nrow(fia_matches) > 0  -->
<!--   small_di_s_n$in_not_fia[i] = nrow(not_fia_matches) > 0  -->

<!-- } -->

<!-- small_di_s_n <- filter(small_di_s_n, in_fia, in_not_fia) -->

<!-- set.seed(1977) -->

<!-- subsamples <- list() -->

<!-- for(i in 1:nrow(small_di_s_n)) { -->

<!--   this_s0 = small_di_s_n$s0[i] -->
<!--   this_n0 = small_di_s_n$n0[i] -->

<!--   fia_matches = filter(fia, s0 == this_s0, n0 == this_n0) -->

<!--   not_fia_matches = filter(not_fia, s0 == this_s0, n0 == this_n0) -->

<!--   n_to_draw = min(nrow(fia_matches), nrow(not_fia_matches)) -->

<!--   fia_draw = sample.int(n = nrow(fia_matches), size = n_to_draw, replace = F) -->
<!--   not_fia_draw = sample.int(n = nrow(not_fia_matches), size = n_to_draw, replace = F) -->

<!--   subsamples[[i]] <- (bind_rows(fia_matches[fia_draw,], not_fia_matches[not_fia_draw, ])) -->

<!-- } -->

<!-- sub_di <- bind_rows(subsamples) %>% -->
<!--   mutate(Dataset = ifelse(fia_yn == "fia", "FIA", "Other datasets")) -->

<!-- simpson_ks <- filter(sub_di, nparts > 40) %>% -->
<!--   select(simpson_95_ratio_1t, Dataset, simpson_percentile, s0, n0) %>%  -->
<!--   group_by(Dataset, s0, n0) %>% -->
<!--   mutate(pairing = dplyr::row_number()) %>% -->
<!--   ungroup() %>% -->
<!--   tidyr::pivot_wider(id_cols = c(s0, n0, pairing), names_from = Dataset, values_from = c(simpson_95_ratio_1t, simpson_percentile)) -->

<!-- simpson_breadth <- ks.test(simpson_ks$simpson_95_ratio_1t_FIA, simpson_ks$`simpson_95_ratio_1t_Other datasets`) -->

<!-- simpson_percent <- ks.test(simpson_ks$simpson_percentile_FIA, simpson_ks$`simpson_percentile_Other datasets`) -->
<!-- simpson_breadth -->
<!-- simpson_percent -->

<!-- skewness_ks <- filter(sub_di, nparts > 40) %>% -->
<!--   select(skew_95_ratio_1t, Dataset, skew_percentile, s0, n0) %>%  -->
<!--   group_by(Dataset, s0, n0) %>% -->
<!--   mutate(pairing = dplyr::row_number()) %>% -->
<!--   ungroup() %>% -->
<!--   tidyr::pivot_wider(id_cols = c(s0, n0, pairing), names_from = Dataset, values_from = c(skew_95_ratio_1t, skew_percentile)) -->

<!-- skewness_breadth <- ks.test(skewness_ks$skew_95_ratio_1t_FIA, skewness_ks$`skew_95_ratio_1t_Other datasets`) -->

<!-- skewness_percent <- ks.test(skewness_ks$skew_percentile_FIA, skewness_ks$`skew_percentile_Other datasets`) -->
<!-- skewness_breadth -->
<!-- skewness_percent -->

<!-- fig_4 <- gridExtra::grid.arrange(grobs = list( -->
<!--   ggplot(filter(sub_di, nparts > 20), aes(skew_95_ratio_1t)) + -->
<!--     geom_histogram()+ -->
<!--     theme_bw() + -->
<!--     facet_wrap(vars(Dataset), scales = "free_y")  + -->
<!--     xlab("Breadth index") + -->
<!--     ylab("Number of communities") + -->
<!--     ggtitle("Breadth index", subtitle = "Skewness"), -->

<!--   ggplot(filter(sub_di, nparts > 20), aes(simpson_95_ratio_1t)) + -->
<!--     geom_histogram()+ -->
<!--     theme_bw() + -->
<!--     facet_wrap(vars(Dataset), scales = "free_y")  + -->
<!--     xlab("Breadth index") + -->
<!--     ylab("") + -->
<!--     ggtitle("", subtitle = "Evenness"), -->

<!--   ggplot(filter(sub_di, nparts > 20), aes(skew_percentile_excl)) + -->
<!--     geom_histogram()+ -->
<!--     theme_bw() + -->
<!--     facet_wrap(vars(Dataset), scales = "free_y")  + -->
<!--     xlab("Percentile rank") + -->
<!--     ylab("Number of communities") + -->
<!--     ggtitle("Percentile rank", subtitle = "Skewness"), -->

<!--   ggplot(filter(sub_di, nparts > 20), aes(simpson_percentile)) + -->
<!--     geom_histogram()+ -->
<!--     theme_bw() + -->
<!--     facet_wrap(vars(Dataset), scales = "free_y")  + -->
<!--     xlab("Percentile rank") + -->
<!--     ylab("")+ -->
<!--     ggtitle("", subtitle = "Evenness")), ncol = 2, top = textGrob("Figure 4", gp = gpar(fill = "white"))) -->

<!-- plot(fig_4) -->

<!-- ``` -->

<!-- ```{r} -->
<!-- pdf("figure_1.pdf", title = "Figure 1", bg = "white", paper = "letter", width = 6.5, height = 6.5) -->
<!-- gridExtra::grid.arrange(grobs = breadth_plots, ncol = 2, top = textGrob("Figure 1", gp = gpar(fill = "white"))) -->
<!-- dev.off() -->

<!-- pdf("figure_2.pdf", title = "Figure 2", bg = "white", paper = "letter", width = 6.5, height = 6.5) -->
<!--  gridExtra::grid.arrange(grobs = list( -->

<!--   ggplot(filter(all_di, s0 > 2, nparts > 20), aes(skew_percentile_excl)) + -->
<!--     geom_histogram(bins = 100) + -->
<!--     geom_vline(xintercept = 95, color = "red") + -->
<!--     theme_bw() + -->
<!--     facet_wrap(vars(Dataset), scales = "free_y", ncol = 1) + ggtitle("Skewness") + -->
<!--     xlab("") + -->
<!--     ylab(""),# + -->
<!--   #  xlab("Percentile rank of observed value relative to feasible set") + -->
<!--     #ylab("Number of communities") , -->

<!--   ggplot(filter(all_di, nparts > 20), aes(simpson_percentile)) +  -->
<!--     geom_histogram(bins = 100) + -->
<!--     geom_vline(xintercept = 5, color = "red") + -->
<!--     theme_bw() + -->
<!--     facet_wrap(vars(Dataset), scales = "free_y", ncol = 1) + ggtitle("Evenness") +  -->
<!--     xlab("") + -->
<!--     ylab("")#+ -->
<!--     #xlab("Percentile rank of observed value relative to feasible set") + -->
<!--   #  ylab("Number of communities") -->
<!-- ), ncol = 2, -->
<!-- top = textGrob("Figure 2", gp = gpar(fill = "white")), left = textGrob("Number of communities", rot = 90, gp = gpar(fill = "black")), -->
<!-- bottom = textGrob("Percentile rank of observed value relative to feasible set"), gp = gpar(fill = "white")) -->
<!--  dev.off() -->

<!-- pdf("figure_3.pdf", title = "Figure 3", bg = "white", paper = "letter", width = 6.5, height = 6.5) -->
<!-- gridExtra::grid.arrange(grobs = list( -->
<!--   ggplot(filter(all_di, s0 > 2, nparts > 20), aes(x= skew_95_ratio_1t)) + -->
<!--     geom_histogram() + -->
<!--     theme_bw() + -->
<!--     facet_wrap(vars(Dataset), scales = "free_y", ncol = 1) + -->
<!--     xlab("") + -->
<!--     ylab("") + -->
<!--     ggtitle("Skewness") + -->
<!--     xlim(0, 1), -->

<!--   ggplot(filter(all_di, nparts > 20), aes(x = simpson_95_ratio_1t)) + -->
<!--     geom_histogram() + -->
<!--     theme_bw() + -->
<!--     facet_wrap(vars(Dataset), scales = "free_y", ncol = 1) + -->
<!--     xlab("") + -->
<!--     ylab("") + -->
<!--     ggtitle("Evenness") + -->
<!--     xlim(0, 1) -->
<!-- ), ncol = 2, -->
<!-- top = textGrob("Figure 3", gp = gpar(fill = "white")), -->
<!-- left = "Number of communities",  -->
<!-- bottom = "Breadth index (ranges 0-1, with 1 being very broad)") -->

<!-- dev.off() -->

<!-- pdf("figure_4.pdf", title = "Figure 4", bg = "white", paper = "letter", width = 6.5, height = 6.5) -->
<!--  gridExtra::grid.arrange(grobs = list( -->
<!--   ggplot(filter(sub_di, nparts > 20), aes(skew_95_ratio_1t)) + -->
<!--     geom_histogram()+ -->
<!--     theme_bw() + -->
<!--     facet_wrap(vars(Dataset), scales = "free_y")  + -->
<!--     xlab("Breadth index") + -->
<!--     ylab("Number of communities") + -->
<!--     ggtitle("Breadth index", subtitle = "Skewness"), -->

<!--   ggplot(filter(sub_di, nparts > 20), aes(simpson_95_ratio_1t)) + -->
<!--     geom_histogram()+ -->
<!--     theme_bw() + -->
<!--     facet_wrap(vars(Dataset), scales = "free_y")  + -->
<!--     xlab("Breadth index") + -->
<!--     ylab("") + -->
<!--     ggtitle("", subtitle = "Evenness"), -->

<!--   ggplot(filter(sub_di, nparts > 20), aes(skew_percentile_excl)) + -->
<!--     geom_histogram()+ -->
<!--     theme_bw() + -->
<!--     facet_wrap(vars(Dataset), scales = "free_y")  + -->
<!--     xlab("Percentile rank") + -->
<!--     ylab("Number of communities") + -->
<!--     ggtitle("Percentile rank", subtitle = "Skewness"), -->

<!--   ggplot(filter(sub_di, nparts > 20), aes(simpson_percentile)) + -->
<!--     geom_histogram()+ -->
<!--     theme_bw() + -->
<!--     facet_wrap(vars(Dataset), scales = "free_y")  + -->
<!--     xlab("Percentile rank") + -->
<!--     ylab("")+ -->
<!--     ggtitle("", subtitle = "Evenness")), ncol = 2, top = textGrob("Figure 4", gp = gpar(fill = "white"))) -->
<!-- dev.off() -->
<!-- ``` -->

>>>>

---
title: "Figures and results for main manuscript"
author: Renata Diaz
date: "`r Sys.Date()`"
output: 
    github_document:
       df_print: kable
       toc: true
---

@@

```{r first hists, fig.dim = c(10,5)}

@@

  plot_percentile_hist(all_di, "real_po_percentile_mean", "Dissimilarity to the \ncentral tendency", facetvar = "Dataset", tails = 1),
  plot_percentile_hist(all_di, "nsingletons_percentile_mean", "\nNumber of rare species", facetvar = "Dataset"),
  plot_percentile_hist(all_di, "skew_percentile_mean", "\nSkewness", facetvar = "Dataset", min_s0 = 3),
  plot_percentile_hist(all_di, "simpson_percentile_mean", "\nSimpson evenness", facetvar = "Dataset"),
  plot_percentile_hist(all_di, "shannon_percentile_mean", "\nShannon diversity", facetvar = "Dataset")
), ncol = 5,
top = textGrob("Figure 2", gp = gpar(fill = "white")), left = textGrob("Number of communities", rot = 90, gp = gpar(fill = "black")),
bottom = textGrob("Percentile rank of observed value relative to feasible set"), gp = gpar(fill = "white"))
```

@@

  if(grepl("sim_pos", yvar)) {
    min_nparts = 20
    ylabel = "Mean dissimilarity"
  } else {
    min_nparts = 40
    ylabel = "Breadth index"
  }

@@

  ggplot(di_df, aes(nparts, response, color = Dataset)) +
    geom_point(alpha = .3) +
    geom_point(data = filter(di_df, s0 < 0)) +
    scale_color_viridis_d(end = .9) +
    xlab("") +
    ylab(ylabel) +
    scale_x_log10() +
    ggtitle(yvar_name) + 
    theme(legend.position = "none")+ 
    theme(plot.title = element_text(size=10))
}

@@

gridExtra::grid.arrange(grobs = list(
  plot_narrowness(all_di, "sim_pos_from_best", "Dissimilarity \nto central tendency") + ylab("Mean dissimilarity") + theme(legend.position = "bottom", legend.direction = "vertical" , legend.margin = margin(b = .25, r = 0, t = 0, l = 0, unit = "in")), 
  gridExtra::grid.arrange(grobs = list(
    plot_narrowness(all_di, "skew_95_ratio_2t", "\nSkewness"),
    plot_narrowness(all_di, "simpson_95_ratio_2t", "\nSimpson evenness")+ ylab(""),
    plot_narrowness(all_di, "nsingletons_95_ratio_2t", "\nNumber of rare species"),
       plot_narrowness(all_di, "shannon_95_ratio_2t", "\nShannon diversity") + ylab("")
  ), ncol = 2)), ncol = 2, widths = c( 2, 4), bottom = textGrob("Number of elements in the feasible set"))

@@

```{r}

plot_narrowness_hist <- function(di_df, col_name, plot_name, facetvar = "Dataset", min_s0 = 0) {

  if(grepl("sim_pos", col_name)) {
    xvarname = "Mean dissimilarity"
    min_nparts = 40
  } else {
    min_nparts = 20
    xvarname = "Breadth index"
  }

  ggplot(filter(di_df, nparts > min_nparts, s0 >= min_s0), aes(response)) +
    geom_histogram(bins = 40, boundary = 100) +
    theme_bw() +
    ylab("") +
    xlab(xvarname) +
    ggtitle( plot_name) +
    facet_wrap(vars(facetvar), ncol = 1, scales = "free_y")+ 
    theme(plot.title = element_text(size=10))

```{r, fig.dim = c(10,5)}

  plot_narrowness_hist(all_di, "sim_pos_from_best", "Dissimilarity to the \ncentral tendency", facetvar = "Dataset"),
  plot_narrowness_hist(all_di, "nsingletons_95_ratio_2t", "\nNumber of rare species", facetvar = "Dataset"),
  plot_narrowness_hist(all_di, "skew_95_ratio_2t", "\nSkewness", facetvar = "Dataset", min_s0 = 3),
  plot_narrowness_hist(all_di, "simpson_95_ratio_2t", "\nSimpson evenness", facetvar = "Dataset"),
  plot_narrowness_hist(all_di, "shannon_95_ratio_2t", "\nShannon diversity", facetvar = "Dataset")
), ncol = 5,
 left = textGrob("Number of communities", rot = 90, gp = gpar(fill = "black")), gp = gpar(fill = "white"))

# Comparison of FIA and comparably sized communities (Figure 4)

```{r, fig.dim = c(10, 5)}

fia_max_s = max(filter(all_di, dat == "fia")$s0)
fia_max_n = max(filter(all_di, dat == "fia")$n0)

fia = filter(all_di, dat == "fia")

small_di <- all_di %>%
  filter(s0 <= fia_max_s,
         n0 <= fia_max_n) %>%
  mutate(fia_yn = ifelse(dat == "fia", "fia", "other datasets"),
         right_corner = FALSE)

for(i in 1:nrow(small_di)) {
  if(small_di$dat[i] != "fia") {
    fia_match_s0 = filter(fia, s0 >= small_di$s0[i])

    max_n0_for_this_s0 = max(fia_match_s0$n0)

    small_di$right_corner[i] = small_di$n0[i] > max_n0_for_this_s0

  }
}

small_di <- small_di %>%
  filter(!right_corner)
not_fia <- filter(small_di, fia_yn != "fia")
fia = filter(small_di, dat == "fia")

small_di_s_n <- small_di %>%
  select(s0, n0) %>%
  distinct() %>%
  mutate(in_fia = FALSE,
         in_not_fia = FALSE)

for(i in 1:nrow(small_di_s_n)) {

  this_s0 = small_di_s_n$s0[i]
  this_n0 = small_di_s_n$n0[i]

  fia_matches = filter(fia, s0 == this_s0, n0 == this_n0)
  not_fia_matches = filter(not_fia, s0 == this_s0, n0 == this_n0)

  small_di_s_n$in_fia[i] = nrow(fia_matches) > 0
  small_di_s_n$in_not_fia[i] = nrow(not_fia_matches) > 0

small_di_s_n <- filter(small_di_s_n, in_fia, in_not_fia)

set.seed(1977)

subsamples <- list()

for(i in 1:nrow(small_di_s_n)) {

  this_s0 = small_di_s_n$s0[i]
  this_n0 = small_di_s_n$n0[i]

  fia_matches = filter(fia, s0 == this_s0, n0 == this_n0)

  not_fia_matches = filter(not_fia, s0 == this_s0, n0 == this_n0)

  n_to_draw = min(nrow(fia_matches), nrow(not_fia_matches))

  fia_draw = sample.int(n = nrow(fia_matches), size = n_to_draw, replace = F)
  not_fia_draw = sample.int(n = nrow(not_fia_matches), size = n_to_draw, replace = F)

  subsamples[[i]] <- (bind_rows(fia_matches[fia_draw,], not_fia_matches[not_fia_draw, ]))

sub_di <- bind_rows(subsamples) %>%
  mutate(Dataset = ifelse(fia_yn == "fia", "FIA", "Other datasets"))

fia_di <- filter(sub_di, fia_yn == "fia")
other_di <- filter(sub_di, fia_yn != "fia")

ks_compare <- function(fia_df, other_df, compare_var) {

  if(grepl("skew", compare_var)) {
    fia_df <- filter(fia_df, s0 > 2)
    other_df <- filter(fia_df, s0 >2)
  }

  if(grepl("sim_pos", compare_var)) {
    fia_df <- filter(fia_df, nparts > 20)
    other_df <- filter(other_df, nparts > 20)
  } else {
      fia_df <- filter(fia_df, nparts > 40)
    other_df <- filter(other_df, nparts > 40)
  }

  kstest <- ks.test(fia_df[[compare_var]], other_df[[compare_var]])

  return(data.frame(
    var = compare_var,
    d = kstest$statistic,
    p = kstest$p.value
  ))
}

simpson_rat_ks <- ks_compare(fia_di, other_di, "simpson_95_ratio_2t")
skew_rat_ks <- ks_compare(fia_di, other_di, "skew_95_ratio_2t")
shannon_rat_ks <- ks_compare(fia_di, other_di, "shannon_95_ratio_2t")
nsingletons_rat_ks <- ks_compare(fia_di, other_di, "nsingletons_95_ratio_2t")
diss_rat_ks <- ks_compare(fia_di, other_di, "sim_pos_from_best")

bind_rows(simpson_rat_ks, skew_rat_ks, shannon_rat_ks, nsingletons_rat_ks, diss_rat_ks)

simpson_perc_ks <- ks_compare(fia_di, other_di, "simpson_percentile")
skew_perc_ks <- ks_compare(fia_di, other_di, "skew_percentile_excl")
shannon_perc_ks <- ks_compare(fia_di, other_di, "shannon_percentile")
nsingletons_perc_ks <- ks_compare(fia_di, other_di, "nsingletons_percentile_excl")
diss_perc_ks <- ks_compare(fia_di, other_di, "real_po_percentile_excl")

bind_rows(simpson_perc_ks, skew_perc_ks, shannon_perc_ks, nsingletons_perc_ks, diss_perc_ks)

  plot_percentile_hist(sub_di, "real_po_percentile_mean", "Dissimilarity to the \ncentral tendency", facetvar = "Dataset", tails = 1),
  plot_percentile_hist(sub_di, "nsingletons_percentile_mean", "\nNumber of rare species", facetvar = "Dataset"),
  plot_percentile_hist(sub_di, "skew_percentile_mean", "\nSkewness", facetvar = "Dataset", min_s0 = 3),
  plot_percentile_hist(sub_di, "simpson_percentile_mean", "\nSimpson evenness", facetvar = "Dataset"),
  plot_percentile_hist(sub_di, "shannon_percentile_mean", "\nShannon diversity", facetvar = "Dataset")
), ncol = 5,
top = textGrob("Figure 2", gp = gpar(fill = "white")), left = textGrob("Number of communities", rot = 90, gp = gpar(fill = "black")),
bottom = textGrob("Percentile rank of observed value relative to feasible set"), gp = gpar(fill = "white"))

  plot_narrowness_hist(sub_di, "sim_pos_from_best", "Dissimilarity to the \ncentral tendency", facetvar = "Dataset"),
  plot_narrowness_hist(sub_di, "nsingletons_95_ratio_2t", "\nNumber of rare species", facetvar = "Dataset"),
  plot_narrowness_hist(sub_di, "skew_95_ratio_2t", "\nSkewness", facetvar = "Dataset", min_s0 = 3),
  plot_narrowness_hist(sub_di, "simpson_95_ratio_2t", "\nSimpson evenness", facetvar = "Dataset"),
  plot_narrowness_hist(sub_di, "shannon_95_ratio_2t", "\nShannon diversity", facetvar = "Dataset")
), ncol = 5,
 left = textGrob("Number of communities", rot = 90, gp = gpar(fill = "black")), gp = gpar(fill = "white"))

diss_results <- sub_di %>%
  filter(nparts > 20) %>%
  group_by(Dataset) %>%
  summarize(high_diss = mean(real_po_percentile_excl > 95),
            nsites = dplyr::n()) %>%
  ungroup() %>%
  mutate(`High dissimilarity` = paste0(signif(100 * high_diss, 2), "%; n = ", nsites)) %>%
  select(-nsites)

skew_results <- sub_di %>%
  filter(nparts > 40, s0 > 2) %>%
  group_by(Dataset) %>%
  summarize(high_skew = mean(skew_percentile_excl > 97.5),
            low_skew = mean(skew_percentile < 2.5),
            nsites = dplyr::n()) %>%
  ungroup() %>%
  mutate(`High skew` = paste0(signif(100 * high_skew, 2), "%; n = ", nsites),
         `Low skew` = paste0(signif(100 * low_skew, 2), "%; n = ", nsites)) %>%
  select(-nsites)

metric_results <- sub_di %>%
  filter(nparts > 40) %>%
  group_by(Dataset) %>%
  summarize(high_simpson = mean(simpson_percentile_excl > 97.5),
            low_simpson = mean(simpson_percentile < 2.5),
            high_shannon = mean(shannon_percentile_excl > 97.5),
            low_shannon = mean(shannon_percentile < 2.5),
            high_nsingletons = mean(nsingletons_percentile_excl > 97.5),
            low_nsingletons = mean(nsingletons_percentile < 2.5),
            nsites = dplyr::n()) %>%
  ungroup() %>%
  mutate(`High Simpson` = paste0(signif(100 * high_simpson, 2), "%; n = ", nsites),
         `Low Simpson` = paste0(signif(100 * low_simpson, 2), "%; n = ", nsites),
         `High Shannon` = paste0(signif(100 * high_shannon, 2), "%; n = ", nsites),
         `Low Shannon` = paste0(signif(100 * low_shannon, 2), "%; n = ", nsites),
         `High proportion of rare species` = paste0(signif(100 * high_nsingletons, 2), "%; n = ", nsites),
         `Low proportion of rare species` = paste0(signif(100 * low_nsingletons, 2), "%; n = ", nsites)) %>%
  select(-nsites)
